\plaintitle

### 2017-06-06 papers/IoT2017/services.tex
no message

We can employ well-known and widely used techniques for anonymous communication, such as \emph{onion routing}~\cite{reed1998anonymous}.
To build an onion network, the smart meters, prosumers, and other devices can act as onion routers, and the list of onion routers in a microgrid can be published on the ledger.
In practice, this service can built on 
%In our first implementation, we can use
 the free and open-source Tor software with private Directory Authorities.
In this case, anonymous communication addresses in bids and asks correspond to public-keys that identify Tor hidden services.
% ritter.vg: "run your own tor network"
% https://ritter.vg/blog-run_your_own_tor_network.html

@@

\subsubsection{Bidding Anonymity}
Finally, we must provide prosumers with the ability to post energy bids and asks anonymously.
To this end, we create a storage for anonymous bids that is readable by all the prosumers in the microgrid.
Any prosumer may submit a bid to this storage; however, in order to do so, they must provide a zero-knowledge proof of owning the assets that are to be traded:
\begin{itemize}
\item To submit an energy sell bid, the prosumer must prove that it owns an energy production asset on the chain.
\item To submit an energy buy bid, the prosumer must prove that it own an energy consumption asset as well as financial assets on the chain.
\end{itemize}

>>>>

We can employ well-known and widely used techniques for anonymous communication, such as \emph{onion routing}~\cite{reed1998anonymous}.
To build an onion network, the smart meters, prosumers, and other devices can act as onion routers, and the list of onion routers in a microgrid can be published on the ledger.
In practice, this service can built on 
%In our first implementation, we can use
 the free and open-source Tor software with private Directory Authorities.
In this case, anonymous communication identifiers in bids and asks correspond to public-keys that identify Tor hidden services.
% ritter.vg: "run your own tor network"
% https://ritter.vg/blog-run_your_own_tor_network.html

@@

\subsubsection{Bidding Anonymity}
Finally, we must enable prosumers to anonymously post energy bids and asks on the bid storage service.
An anonymous bid (or ask) contains an ECA (or EPA), a price, and an anonymous communication identifier (e.g., Tor hidden service), which can be used to contact the bidding (or asking) prosumer.
To enforce safety requirements, the bid storage service must verify that the prosumer actually owns the asset to be traded.
To this end, the prosumer first has to prove that it controls the anonymous address where the asset is stored, which can be performed in multiple ways.
In many distributed ledgers, an address represents a public key, and controlling means knowing the corresponding private key.
In this case, the prosumer can prove that it controls an address by signing a challenge, which was freshly generated by the service, with the private key of the address.
Alternatively, the prosumer may also prove control by transferring zero amount of assets to a random address that was freshly generated by the service.

%Finally, we must provide prosumers with the ability to post energy bids and asks anonymously.
%To this end, we create a storage for anonymous bids that is readable by all the prosumers in the microgrid.
%Any prosumer may submit a bid to this storage; however, in order to do so, they must provide a zero-knowledge proof of owning the assets that are to be traded:
%\begin{itemize}
%\item To submit an energy sell bid, the prosumer must prove that it owns an energy production asset on the chain.
%\item To submit an energy buy bid, the prosumer must prove that it own an energy consumption asset as well as financial assets on the chain.
%\end{itemize}

### 2017-06-06 papers/IoT2017/solution.tex
no message

\draw[transfer] (smartmeter) -- node [asset, above] {\circled{1} energy\\production asset} (prosumer1);
\draw[transfer] (prosumer1) -- node [asset, above] {\circled{2} energy\\production asset} (mixing1);
\draw[transfer] (mixing1) -- node [asset, above] {\circled{3} energy\\production asset} (prosumer2);
\draw[transfer, dashed] (prosumer2) -- node [asset, above right] {\circled{4} energy production asset,\\energy ask} (bidstorage);
\draw[transfer, dashed] (bidstorage) -- node [asset, below right] {energy\\ask} (partner);
\draw[transfer, bend right=30] (partner) to node [asset, below] {\circled{5} financial asset,\\energy consumption asset} (prosumer3);
\draw[transfer, bend right=50] (prosumer2) to node [asset, right, yshift=0.25em] {\circled{5} energy\\production asset} (partner);
\draw[transfer] (prosumer3) -- node [asset, below] {\circled{6} financial asset,\\
energy consumption asset} (smartmeter2);
\end{tikzpicture}
\vspace{-1em}
\caption{Simplified overview of the flow of assets from the perspective of a prosumer who sells energy. Note that in order to prevent de-anonymization, a prosumer should use multiple addresses and multiple rounds of mixing.}
\label{fig:sellFlow}
\end{figure*}

@@

Now, the prosumer can engage in energy trading anonymously.
To find a trade partner, it can either post an \emph{energy ask} on the bid storage, or simply search the storage for an acceptable \emph{energy bid}.
To post an energy ask, the prosumer first proves to the storage service -- without revealing its original identity -- that it owns a production asset stored at an anonymous address.
It can then post the energy ask \circled{4}, which contains an anonymous communication address\footnote{We discuss communication anonymity later.}, a price, and a reference to the production asset.
If another prosumer, who would like to buy energy, finds the ask acceptable, it can contact the selling prosumer at the communication address given by the ask.

@@

Second, consider a prosumer who would like to buy energy from another prosumer.
Since the trading process is very similar to the case of the selling prosumer, we will discuss only the differences.
In the first step, the prosumer tries to withdraw a financial asset and an energy consumption asset from its smart meter.
If the prosumer has the consumption capacity and good financial standing, the smart meter transfers the assets to the prosumer and adds the financial amount to the prosumer's bill.
After transferring the assets through a mixing service, the prosumer is ready to post an energy bid on the bid service.
To do so, it first proves the ownership of both the financial asset and the consumption asset to the service, and then posts the energy bid, which includes an anonymous communication address.
If a partner is found, the trade is executed as described before, the prosumer playing the role of the buyer.
Finally, the prosumer deposits the purchased energy production asset to the anonymous address of its smart meter,
which credits the energy amount to the prosumer, for billing purposes.
Note that if the prosumer has not used up the financial asset completely, then the remainder may also be deposited back to the smart meter.

>>>>

\draw[transfer] (smartmeter) -- node [asset, above] {\circled{1} energy\\production asset} (prosumer1);
\draw[transfer] (prosumer1) -- node [asset, above] {\circled{2} energy\\production asset} (mixing1);
\draw[transfer] (mixing1) -- node [asset, above] {\circled{3} energy\\production asset} (prosumer2);
\draw[transfer, dashed] (prosumer2) -- node [asset, above right, xshift=-1.5em, yshift=0.5em] {\circled{4} energy production asset,\\energy ask} (bidstorage);
\draw[transfer, dashed] (bidstorage) -- node [asset, below right] {energy\\ask} (partner);
\draw[transfer, bend right=30] (partner) to node [asset, below] {\circled{5} financial asset,\\energy consumption asset} (prosumer3);
\draw[transfer, bend right=50] (prosumer2) to node [asset, right, yshift=0.25em] {\circled{5} energy\\production asset} (partner);
\draw[transfer] (prosumer3) -- node [asset, below] {\circled{6} financial asset,\\
energy consumption asset} (smartmeter2);
\end{tikzpicture}
\caption{Simplified overview of the flow of assets from the perspective of a prosumer who sells energy. Note that in order to prevent de-anonymization, a prosumer should use multiple addresses and multiple rounds of mixing.}
\label{fig:sellFlow}
\end{figure*}

@@

Now, the prosumer can engage in energy trading anonymously.
To find a trade partner, it can either post an \emph{energy ask} on the bid storage, or simply search the storage for an acceptable \emph{energy bid}.
To post an energy ask, the prosumer first proves to the storage service -- without revealing its original identity -- that it owns a production asset stored at an anonymous address.
It can then post the energy ask \circled{4}, which contains an anonymous communication identifier\footnote{We discuss communication anonymity later.}, a price, and a reference to the production asset.
If another prosumer, who would like to buy energy, finds the ask acceptable, it can contact the selling prosumer at the communication identifier given by the ask.

@@

Second, consider a prosumer who would like to buy energy from another prosumer.
Since the trading process is very similar to the case of the selling prosumer, we will discuss only the differences.
In the first step, the prosumer tries to withdraw a financial asset and an energy consumption asset from its smart meter.
If the prosumer has the consumption capacity and good financial standing, the smart meter transfers the assets to the prosumer and adds the financial amount to the prosumer's bill.
After transferring the assets through a mixing service, the prosumer is ready to post an energy bid on the bid service.
To do so, it first proves the ownership of both the financial asset and the consumption asset to the service, and then posts the energy bid, which includes an anonymous communication identifier.
If a partner is found, the trade is executed as described before, the prosumer playing the role of the buyer.
Finally, the prosumer deposits the purchased energy production asset to the anonymous address of its smart meter,
which credits the energy amount to the prosumer, for billing purposes.
Note that if the prosumer has not used up the financial asset completely, then the remainder may also be deposited back to the smart meter.
